### 2019-04-11 5_evaluation.tex
Apply Alex's comments.

Spark, Swift/T and TensorFlow
are omitted from comparisons with more complicated dependence
patterns, as the higher overheads of these systems would have required
unreasonably large problem sizes (beyond what can be completed in 6
hours) to reach 50\% efficiency. Regent and X10 are missing from some
graphs as Cori was highly impacted before the deadline.

@@

One advantage of systems with asynchronous execution capabilities is
the ability to mitigate load imbalance, especially in the presence of
task parallelism. To quantify this effect,
Figure~\ref{fig:efficiency-imbalance} plots task granularity vs
efficiency curves under load imbalance where each task's duration is multiplied by a uniform random variable between [0,~1). The task durations are generated with a deterministic
pseudo random number generator with a deterministic seed to ensure
identical task durations for all systems.

>>>>

Spark, Swift/T and TensorFlow
are omitted from comparisons with more complicated dependencies, as the higher overheads of these systems would have required
unreasonably large problem sizes (beyond what can be completed in 6
hours) to reach 50\% efficiency. Regent and X10 are incomplete as Cori was highly impacted before the deadline; complete results will be in the final paper.

@@

One advantage of systems with asynchronous execution capabilities is
the ability to mitigate load imbalance with little or no additional programmer effort, especially in the presence of
task parallelism. To quantify this effect,
Figure~\ref{fig:efficiency-imbalance} plots task granularity vs
efficiency curves under load imbalance where each task's duration is multiplied by a uniform random variable between [0,~1). The task durations are generated with a deterministic
pseudo random number generator with a deterministic seed to ensure
identical task durations for all systems.
